\speculake: Hiding Malware in Speculative Execution

### 2018-11-30 paper/figures.tex
figure updates
edit on fig 8

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering  
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
        \caption{\textbf{Speculative Bandwidth}\,---\,%
        Using the speculative primitive, 1KB of data
        can be decrypted and exfiltrated at a speed between 5 and 6 kbps from
        the speculative world with 20 iterations per round for guaranteed
        correctness.  Varying the width of the channel results in competing
        performance factors, with an optimal throughput achieved at 8~bits.}
    \label{fig:spec_bandwidth}
\end{figure}
}

>>>>

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering  
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
        \caption{\textbf{Speculative Bandwidth}\,---\,%
        Using our speculative primitive, 1KB of data
        can be decrypted and exfiltrated at a speed between 5 and 6~Kbps from
        the speculative world with 20 redundant iterations per round (to ensure
        correctness). Increased channel width exfiltrates more data per round,
        but takes longer to measure the cache side channel. Optimal throughput is
        achieved with an 8-bit channel.}
    \label{fig:spec_bandwidth}
\end{figure}
}
